---
title: "COVID-19 Forecast"
output:
  flexdashboard::flex_dashboard:
    social: menu
    theme: flatly
    logo: covid19_response_icon.png
    css: styles.css
runtime: shiny
resource_files:
- setup.R
- covid19_response_icon.png
- styles.css
---


```{r setup, include=FALSE, code = readLines("setup.R")}
```


Forecast {data-orientation=rows, data-icon="fa-line-chart"}
=====================================  

Configuration {.sidebar}
-------------------------------------
### Forecast configuration
```{r}
renderUI({
  models <- calibration_table() %>% collect %>% .[[".model_id"]]
  names(models) <- calibration_table() %>% collect %>% .[[".model_desc"]]
  
  selectInput('model', 'Model', models)
})

checkboxInput('all_models', 'All models', value = TRUE)

numericInput('forecast', 'Months as the forecast set', 3,
              min = 1, max = 12)

strong(hr())
```
Use the __Model builder__ tab to build, train and test your models.

Use the __Forecast__ tab to examine your forecasts.  

Application author: [Adrien BORDERON](https://www.linkedin.com/in/aborderon/)

```{r}
strong(hr())
```

### Data Source

[Our World in Data Github](https://ourworldindata.org/coronavirus)


Row {data-height=600}
-------------------------------------
    
### Forecast
    
```{r}
renderPlotly({
  
  if (input$all_models == FALSE) {
    calibration_table() %>%
    
    filter(.model_id == input$model) %>%
  
    # Refit and Forecast Forward
    modeltime_refit(covid19_confirmed_global_tbl()) %>%
    modeltime_forecast(h = paste(input$forecast, "months"), actual_data = covid19_confirmed_global_tbl()) %>%
    plot_modeltime_forecast(.interactive = FALSE)
  } else {
    calibration_table() %>%
  
    # Refit and Forecast Forward
    modeltime_refit(covid19_confirmed_global_tbl()) %>%
    modeltime_forecast(h = paste(input$forecast, "months"), actual_data = covid19_confirmed_global_tbl()) %>%
    plot_modeltime_forecast(.interactive = FALSE)
  }
})
```

Model builder {data-orientation=rows, data-icon="fa-cogs"}
=====================================
Column {.sidebar}
-------------------------------------
### Dataset configuration
```{r}
selectInput('country', 'Country filter', unique(data_daily$location), selected= "World")

selectInput('dimension', 'Dimension filter', 
                  c("New cases" = 'new_cases',
                    "New deaths" = 'new_deaths',
                    "Total cases" = 'total_cases',
                    "Total deaths" = 'total_deaths'), selected= 'new_cases')

numericInput('testing', 'Days as the testing set', 30,
              min = 1, max = 90)
```
```{r}
strong(hr())
```

### Prophet and XGBoost 
```{r}
selectInput("yearly_seasonality", "Yearly seasonality",
                c("Auto" = 'auto',
                  "True" = TRUE,
                  "False" = FALSE), selected= FALSE)

selectInput("weekly_seasonality", "Weekly seasonality",
                c("Auto" = 'auto',
                  "True" = TRUE,
                  "False" = FALSE), selected= TRUE)

selectInput("daily_seasonality", "Daily seasonality",
                c("Auto" = 'auto',
                  "True" = TRUE,
                  "False" = FALSE), selected= FALSE)
```
```{r}
strong(hr())
```

### Random Forest
```{r}
numericInput('random_forest_trees', 'Number of trees', 500)
numericInput('random_forest_min_n', 'Minimum number of data points in a node', 50)
```
   
Row  {data-height=600}
-------------------------------------
   
### COVID-19 Dataset

```{r}
renderPlotly({
  covid19_confirmed_global_tbl() %>%
    plot_time_series(date, value, .interactive = FALSE)
})

```


### Train/test split time serie
    
```{r}

renderPlotly({
  splits() %>%
    tk_time_series_cv_plan() %>%
    plot_time_series_cv_plan(date, value, .interactive = FALSE)
})
```

Row  {data-height=600}
-------------------------------------
   
### Forecast (Testing Set)

```{r}
renderPlotly({
  calibration_table() %>%
    modeltime_forecast(actual_data = covid19_confirmed_global_tbl()) %>%
    plot_modeltime_forecast(.interactive = FALSE)
})

```

### Accuracy (Testing Set)
    
```{r}
renderTable({
  calibration_table() %>%
    modeltime_accuracy() %>%
    table_modeltime_accuracy(.interactive = FALSE)
})
```

Anomaly Diagnostics {data-orientation=rows, data-icon="fa-tachometer"}
=====================================
Row {data-height=600}
-------------------------------------
### Seasonality
```{r}
renderPlotly({
  covid19_confirmed_global_tbl() %>%
    plot_seasonal_diagnostics(date, value, .interactive = FALSE)
})
```

### Autocorrelation, partial autocorrelation
```{r}
renderPlotly({
  covid19_confirmed_global_tbl() %>%
    plot_acf_diagnostics(date, value, .lags = "1 week", .interactive = FALSE)
})
```


Dataset {data-orientation=rows, data-icon="fa-table"}
=====================================
Row {data-height=600}
-------------------------------------
### Dataset COVID-19 - Our World in Data
```{r}
renderDataTable({
  dataset <- datatable(data_daily %>% select(date, iso_code, continent, location, total_cases, total_deaths, new_cases, new_deaths),
                   filter = "top",
                   options = list(
                       pageLength = 20
                   ))
  dataset
})

```